---
title: "BANL6625- Mid Exam"
author: "Prashanth"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
setwd("D:/Data Mining")
my_data=read.csv("my_data.csv")
my_data_df=my_data[,c(1,2,3,4,5,6)]
summary(my_data_df)
sum(is.na(my_data_df))

#removing NA's from the dataset

clean_data=na.omit(my_data_df)
sum(is.na(clean_data))

#Binning the age into age_groups
clean_data$age_group=cut(clean_data$age,breaks = c(0,10,30,50,100),labels = c("baby","young","Adult","Old"))
summary(clean_data)

```

## Box plot and Scatter plot

```{r}

clean_data$location=as.factor(clean_data$location)
clean_data$soap_type=as.factor(clean_data$soap_type)
clean_data$payment_type=as.factor(clean_data$payment_type)

boxpl1=ggplot(data=clean_data,aes(x=soap_type,y=quantity))+geom_boxplot()
boxpl2=ggplot(data=clean_data,aes(x=payment_type,y=quantity))+geom_boxplot()
Scatter1=ggplot(data=clean_data,aes(x=age_group,y=quantity,col=soap_type))+geom_point()
Scatter2=ggplot(data=clean_data,aes(x=age_group,y=quantity,col=location))+geom_point()
boxpl1
boxpl2
Scatter1
Scatter2
```


```{r}
table(clean_data$soap_type)
table(clean_data$location)
table(clean_data$payment_type)
```

As we can see from the values in soap_type single,in location rural, and in payment_type credit card dominates the dataset.


```{r}
ggplot(clean_data, aes(x=location, fill=soap_type)) + 
  geom_bar(position="stack") + 
  labs(title="Soap Types by Region", x="Region", y="Frequency") + 
  scale_fill_discrete(name="Soap Type")

```

As we can see from the plot there are different type of soaps used in different locations. 

In Rural Region - Single soap type is used

In Suburban Region - twin soap type is used

In Urban Region - Liquid soap type is used


```{r}
ggplot(clean_data, aes(x=location, y=age, fill=payment_type)) +
  geom_boxplot() +
  ggtitle("Payment Type by Location and Age")

```

As we can see from the boxplot, different age people from different location choose different type of payment method

```{r}
library(class)
library(caret)
clean_data$location=as.numeric(as.factor(clean_data$location))
clean_data$payment_type=as.numeric(as.factor(clean_data$payment_type))

#Removed customer column for prediction of data
clean_data_sub=subset(clean_data,select=c("soap_type","location","quantity","age","payment_type"))

#divided the data into 70:30 of train and test dataset
train_index <- sample(row.names(clean_data_sub), 0.7*dim(clean_data_sub)[1])  
valid_index <- setdiff(row.names(clean_data_sub), train_index)  
train_df <- clean_data_sub[train_index, ]
valid_df <- clean_data_sub[valid_index, ]
train_norm_df=train_df
valid_norm_df=valid_df
#Standardizing the data
norm_values <- preProcess(train_df[, c(2,3,4)], method=c("center", "scale"))
train_norm_df[, c(2,3,4)] <- predict(norm_values, train_df[, c(2,3,4)])
valid_norm_df[, c(2,3,4)] <- predict(norm_values, valid_df[, c(2,3,4)])

new_data=data.frame(location="urban",quantity=3,age=55,payment_type="credit card")
new_data$location=as.numeric(as.factor(new_data$location))
new_data$payment_type=as.numeric(as.factor(new_data$payment_type))
new_data_norm=predict(norm_values,new_data)

predict_soap_type=knn(train=train_norm_df[,c(2,3,4,5)],test=new_data_norm,cl=train_norm_df$soap_type,k=67)
predict_soap_type
```


The predicted soap_type for a person living in urban region, age of 55, quantity is 3 and payment type is credit card is "Single"

